Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
addressing comments about first couple of paragraphs in zero level discussion

\subsection{Zero-Point}
\label{sec:zp}

@@

Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust by removing the mean cosmic IR 
background, as well as any instrumental offset. Additionally, faint residuals 
of the Solar dipole remain at low frequencies. We will address these issues by 
separately solving two sub-problems: first, fixing the absolute zero level 
relative to external data, and second fitting per-band relative offsets and low
order corrections by correlating the \PLANCK~bands against one another.
%this last sentence needs lots of work

\subsubsection{Absolute Zero Level}
\label{sec:zp_abs}
In \cite{planckdust}, the absolute zero level of infrared thermal dust emission
was set by requiring that \PLANCK~infrared emission tends to zero when 
H\,\textsc{i} is zero, assuming a linear correlation between these two 
measurements at low column density. However, this approach is somewhat
unsatisfying in that there appear to be different slopes of \PLANCK~857 GHz 
versus H\,\textsc{i} for different ranges of H\,\textsc{i} intensity. In 
particular, \PLANCK~857 GHz appears to ``flatten out'' at very low 
H\,\textsc{i}. More quantitavely, we have found using the LAB H\,\textsc{i} 
data \citep{lab} for $-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for 
H\,\textsc{i}$<$70 K km/s is a factor of $\sim$1.9 lower than the best fit 
slope for 110 K km/s $<$H\,\textsc{i}$<$200 K km/s, and as a result the implied
zero-point offsets for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.

>>>>

\subsection{Zero Level}
\label{sec:zp}

@@

Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust by removing the mean cosmic IR 
background (CIB), as well as any instrumental offset. Additionally, faint 
residuals of the Solar dipole remain at low frequencies. We will address these 
issues by separately solving two sub-problems: first, fixing the absolute zero 
level of \PLANCK~857 GHz relative to external data, and second fitting 
100-545 GHz offsets and low order corrections by correlating these 
\PLANCK~bands against \PLANCK~857 GHz.

\subsubsection{Absolute Zero Level}
\label{sec:zp_abs}
In \cite{planckdust}, the absolute zero level of thermal dust emission was set 
by requiring that \PLANCK~infrared emission tends to zero when H\,\textsc{i} is
zero, assuming a linear correlation between these two measurements at low 
column density. However, this approach is somewhat unsatisfying in that there 
appear to be different slopes of \PLANCK~857 GHz versus H\,\textsc{i} for 
different ranges of H\,\textsc{i} intensity. In particular, \PLANCK~857 GHz 
appears to ``flatten out'' at very low H\,\textsc{i}. More quantitavely, we 
have found using the LAB H\,\textsc{i} data \citep{lab} for 
$-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for H\,\textsc{i}$<$70 K km/s
is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
$<$H\,\textsc{i}$<$200 K km/s, and as a result the implied zero-point offsets 
for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.
